A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with Visual Inference

### 2023-03-14 paper_comparison/paper_comparison/paper_comparison.Rmd
title to title case

---
title: |
  A plot is worth a thousand tests: assessing residual diagnostics with visual inference
type: ARTICLE TEMPLATE
author:
  - name: Weihao Li
    affil: a
    email: weihao.li@monash.edu
  - name: Dianne Cook
    affil: a
    email: dicook@monash.edu
  - name: Emi Tanaka
    affil: a
    email: emi.tanaka@monash.edu
  - name: Susan VanderPlas
    affil: b
    email: susan.vanderplas@unl.edu
affiliation:
  - num: a
    address: |
      Department of Econometrics and Business Statistics, Monash University, Clayton, VIC, Australia
  - num: b
    address: |
      Department of Statistics, University of Nebraska, Lincoln, Nebraska, USA
bibliography: paper.bib
abstract: |
  Abstract to fill.
keywords: |
  data visualization; visual inference; hypothesis testing; residual plots;
header-includes: |
  \usepackage{lscape}
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
output: rticles::tf_article
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: |
  A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with Visual Inference
type: ARTICLE TEMPLATE
author:
  - name: Weihao Li
    affil: a
    email: weihao.li@monash.edu
  - name: Dianne Cook
    affil: a
    email: dicook@monash.edu
  - name: Emi Tanaka
    affil: a
    email: emi.tanaka@monash.edu
  - name: Susan VanderPlas
    affil: b
    email: susan.vanderplas@unl.edu
affiliation:
  - num: a
    address: |
      Department of Econometrics and Business Statistics, Monash University, Clayton, VIC, Australia
  - num: b
    address: |
      Department of Statistics, University of Nebraska, Lincoln, Nebraska, USA
bibliography: paper.bib
abstract: |
  Abstract to fill.
keywords: |
  data visualization; visual inference; hypothesis testing; residual plots;
header-includes: |
  \usepackage{lscape}
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
output: rticles::tf_article
editor_options: 
  chunk_output_type: console
---

### 2023-03-14 paper_comparison/paper_comparison/paper_comparison.tex
title to title case

\title{A plot is worth a thousand tests: assessing residual diagnostics
with visual inference}

@@

For non-linearity patterns, the power curve of RESET test climbs
aggressively from 7\% to 84\% as \(log_e(E)\) increases from 0 to 2.5,
while power of other tests respond inactively to the change of effect,
showing that RESET test is much more sensitive to weak non-linear
structure. Meanwhile, no noticeable residual departures can be spotted
from the example residual plots.

@@

This research is enabled by the use of the following \texttt{R}
packages: cli, curl, dplyr, ggplot2, jsonlite, lmtest, mpoly, progress,
tibble, ggmosaic, purrr, tidyr, readr, stringr, here, kableExtra,
patchwork, rcartocolor. The study website is powered by pythonAnywhere
and the Flask web framework. The jsPsych framework is used to create
behavioral experiments that run in our study website.

>>>>

\title{A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics
with Visual Inference}

@@

For non-linearity patterns, the power curve of RESET test climbs
aggressively from 16\% to 100\% as \(log_e(E)\) increases from 0 to 2.5,
while power of other tests respond inactively to the change of effect,
showing that RESET test is much more sensitive to weak non-linear
structure. Meanwhile, no noticeable residual departures can be spotted
from the example residual plots.

@@
